From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-05 Pi+/paper/finite.tex
Add some text in section 4.3

\begin{definition}
  A presentation of a group $G$ is a type $FR$ such that \ldots is a coequaliser.
\end{definition}

@@

We now introduce a presentation of the symmetric group.

\begin{theorem}
  For all $n : \Nat$,
  \[
    Sn(n) \eqv \Lehmer[n]
  \]
\end{theorem}

>>>>

\begin{definition}
  Let $A$ be a type, and $\List(A)$ the free monoid on $A$. The free group $F(A)$ on $A$ is the set-quotient of
  $\List(A + A)$ by the congruence closure of the relation $(\inl(a) \cons \inr(a) \cons \nil) \sim \nil$.
\end{definition}

\begin{proposition}
  Let $\eta : A \to F(A)$ be given by $a \mapsto \inl(a) \cons \nil$. Given any group $G$ with a map $f : A \to G$,
  there is a canonical lifting of $f$ to a group homomorphism $\extend{f} : F(A) \to G$, such that
  $\extend{f} \comp \eta_{A} \htpy f$, that is, the type of group homomorphisms $h : \Grp(F(A),G)$ satisfying
  $h \comp \eta_{A} \htpy f$ is contractible. Equivalently, composition by $\eta_{A}$ is an equivalence
  $\Grp(F(A),G) \eqv (A \to G)$.
\end{proposition}

\begin{definition}
  Let $A$ be a type and $R : A \to A \to \UU$ a binary relation on $A$. The group $G$ presented by
  $\langle A ; R \rangle$ is given by the set-quotient of the free group $F(A)$ by the normal closure $N_{R}$, or
  equivalently, as the coequaliser
  \[\begin{tikzcd}
      FR && FA && G
      \arrow[shift right=2, from=1-1, to=1-3]
      \arrow[shift left=2, from=1-1, to=1-3]
      \arrow[two heads, from=1-3, to=1-5]
    \end{tikzcd}\]
\end{definition}

\todo{Universal property}

@@

We now introduce a presentation of the symmetric group $\Sn$.

\begin{theorem}
  For all $n : \Nat$,
  \[
    \Sn \eqv \Lehmer[n]
  \]
\end{theorem}
